Geometry of Ranked Nearest Neighbour Interchange Space of Phylogenetic Trees

### 2019-11-04 rnni_convexity.tex
Lemma 1 some tweeks + confused about the statement

\begin{lemma}
Let $T$ and $R = [C_1, \ldots, C_{n-2}]$ be two trees and $p:= \findpath (T,R)$ a path from $T$ to $R$.
Let $T' \neq T,R$ be a tree on $p$ such that $C_1, \ldots, C_{k-1}$ are induced by internal nodes of $T'$, but $C_k$ is not.
Then there is always exactly one $\rnni$ move on $T'$ that results in a tree $T''$ such that $\mrca_{T''}(C_i) < \mrca_{T'}(C_i)$.
\label{lemma:mrca_move}
\end{lemma}

>>>>

\begin{lemma}
Let $T$ and $R = [C_1, \ldots, C_{n-2}]$ be two trees and $p = \findpath (T,R)$.
Let $T'$ be a tree on $p$ different from both $T$ and $R$ such that $C_1, \ldots, C_{k-1}$ are induced by internal nodes of $T'$, but $C_k$ is not.
Then there exists exactly one $\rnni$ move on $T'$ that results in a tree $T''$ such that
\todo{What's $i$?}
$\mrca_{T''}(C_i) < \mrca_{T'}(C_i)$.
\label{lemma:mrca_move}
\end{lemma}
